Verifying Demonstrations

### 2018-02-27 paper/SystemModel.tex
change to intro and system model

\section{System model}%
\label{SystemModel}

\subsection{What is \protect\emph{a} protest?}%
\label{WhatIsAProtest}

Protests can vary considerably.
To be able to estimate the participation count for one, we first need to define
what should be counted.

Let us start by considering some examples.
During the demonstrations against the South Korean president in Seoul
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some 
  people stay\textins{ed} for several hours, others just several minutes%
}.
These rallies were all in the same location in the capital and repeated every 
weekend for the duration of a few weeks.
The Women's Marches~\cite{2017WomensMarchesInUS}, on the other hand, occurred 
in parallel in many locations.
We also have the Venezuelan demonstrations where
\blockcquote{2017VenezuelaProtestFrequency}{%
  anti-government demonstrators have staged daily protests across Venezuela%
} while
\blockcquote{AlJazeeraOnVenezuela2017}{%
  pro-government workers sang and danced as they staged a rival march to show 
  their support for the president's controversial plan to rewrite the 
  constitution%
}.
Judging from these examples, the minimal common part is the cause,%
\label{CauseIsTheCommonDenominator}
but there is also a location (or area) that varies over time.

The organizer Alice wants to count everyone who participated at any time and in 
any of the locations~\cite{2016DemonstrationsInSeoul}.
(Whereas police are only interested in the maximum crowd at any point in time, 
to deploy enough personnel for crowd-control.)
We will define a protest as an event that is uniquely identified by its cause 
(\(id\) below), its time interval (\(t\)) and its location (area \(l\)).
More specifically, we will use the following definition.

\begin{definition}[Protest]\label{DefProtest}
  A \emph{subprotest} is a tuple \((cid, t, l)\) where
  \(cid\in \Z_{2^\lambda}\) is the identifier of the cause of the protest,
  \(t = \interval{t_s}{t_e}\subseteq \R\) is a time interval and
  \(l = N_\epsilon(x, y)\subseteq \R^2\) is the location (an 
  \(\epsilon\)-neighbourhood of \((x,y)\)).
  A \emph{protest} is a set of subprotests sharing the same \(id\).
\end{definition}

The protests described above can be captured using this definition by splitting 
them up into subprotests.
Each subprotest will then be captured by our definition and to find the total 
we can just sum up the results.
The same for marches, the marching path can be divided into subprotests with 
locations (or areas) that slightly overlap.

\subsection{What is a proper count?}

Each participant who wants to be counted must submit a participation proof.
The proof must be associated with the protest, i.e.\ its identifier \(cid\), 
time and location must coincide with any of its subprotests.

In practical terms, participants witness each other's particpation
using their smartphones running the protocol described in
Section~\ref{protocol} and uploading their testimony to a blockchain
after the protest.

More formally, we use witnesses to associate the proof to the location by creating a proof 
share.
% XXX what is a witness?
A witness is only allowed to create one proof share per protester.
The proof and its proof shares are stored in a set, as there should be only 
unique proof shares.

@@

We can now define the participation count as follows.
\begin{definition}[Participation count]
  We define the \emph{participation count} of a protest \(cid\) as the 
  cardinality \(|P_{cid}^{s,\theta}|\) of the set of participation proofs \[
    P_{cid}^{s,\theta} = \left\{ p_{i,j} \mid
      j = cid, s(p_{i,j})\geq \theta \right\}
  \] for some strength function \(s\colon \powerset(W)\to \R_+\) and a threshold 
  \(\theta\).
\end{definition}
The strength function \(s\) can be used to e.g.\ regulate trust in witnesses.
One example would be for \(s\) to return the number of proof shares (i.e.\ 
witnesses) and thus let \(\theta\) to be the threshold of the number of required 
witnesses.

>>>>

\section{Defining and formalizing protest and crowd estimation}%
\label{SystemModel}

%\subsection{What is \protect\emph{a} protest?}%
%\label{WhatIsAProtest}

\emph{Defining the concept of protest.} To be able to estimate the participation count for a protest, we first need to define this concept and what should be counted.
Let us start by considering some examples.
During the demonstrations against the South Korean president in Seoul
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some people stay\textins{ed} for several hours, others just several minutes%
}.
These rallies were all in the same location in the capital and repeated every 
weekend for the duration of a few weeks.
The Women's Marches~\cite{2017WomensMarchesInUS}, on the other hand, occurred in parallel in many locations.
We also have the Venezuelan demonstrations in which
\blockcquote{2017VenezuelaProtestFrequency}{%
  anti-government demonstrators have staged daily protests across Venezuela%
} while
\blockcquote{AlJazeeraOnVenezuela2017}{%
  pro-government workers sang and danced as they staged a rival march to show their support for the president's controversial plan to rewrite the constitution%
}.
Judging from these examples, the minimal common part is the cause,%
\label{CauseIsTheCommonDenominator} but there is also a location (or area) that varies over time.

For the rest of the paper, we will refer to the organizer as Alice.
Assume that the objective of Alice is to count everyone who participated at any time and in any of the locations~\cite{2016DemonstrationsInSeoul}\footnote{Note that the objective does not necessarily align with the definition of the police whose interest could be to determine the maximum crowd at any point in time, to deploy enough personnel for crowd-control.}.
Formally, we define a protest as an event that is uniquely identified by its cause (\(id\) below), its time interval (\(t\)) and its location (area \(l\)).
More specifically, we will use the following definition.

\begin{definition}[Protest]\label{DefProtest}
  A \emph{subprotest} is a tuple \((cid, t, l)\) in which \(cid\in \Z_{2^\lambda}\) is the identifier of the cause of the protest,
  \(t = \interval{t_s}{t_e}\subseteq \R\) is a time interval and \(l = N_\epsilon(x, y)\subseteq \R^2\) is the location (an \(\epsilon\)-neighbourhood of \((x,y)\)).
  A \emph{protest} is a set of subprotests sharing the same \(id\).
\end{definition}

The protests described in the previous examples can be captured using this definition by splitting 
them up into subprotests.
Each subprotest will then be captured by our definition and to estimate the total participation to the protest we can just sum up the estimates obtained.
Similarly for march, the marching path can be divided into subprotests with locations (or areas) that slightly overlap.

\emph{Formalizing the notion of crowd estimation.} Each participant who wants to be counted must submit a participation proof.
The proof must be associated with the protest (\emph{i.e.}, its identifier \(cid\)), time and location must coincide with any of its subprotests.

We use other participants, that we called \emph{witnesses} to associate the proof to the location by creating a proof 
share.
A witness is only allowed to create one proof share per protester to avoid the risk of inflation.
The participation proof and its proof shares are stored in a set, as there should be only unique proof shares.

@@

We can now define the participation count as follows.
\begin{definition}[Participation count]
  We define the \emph{participation count} of a protest \(cid\) as the cardinality \(|P_{cid}^{s,\theta}|\) of the set of participation proofs \[
    P_{cid}^{s,\theta} = \left\{ p_{i,j} \mid
      j = cid, s(p_{i,j})\geq \theta \right\}
  \] for some strength function \(s\colon \powerset(W)\to \R_+\) and a threshold 
  \(\theta\).
\end{definition}
The strength function \(s\) can be used to regulate trust in witnesses.
One example would be for \(s\) to return the number of proof shares (\emph{i.e.}, witnesses) and thus let \(\theta\) to be the threshold of the number of required witnesses.

\emph{System model and physical assumptions.}
In practical terms, participants witness each other's particpation using their smartphones running the protocol described in \cref{protocol} and uploading their testimony to a blockchain after the protest. 
Thus, they need connectivity at least to each other during the protest and Internet connectivity after.

\include*{MANETs}

### 2018-02-27 paper/intro.tex
change to intro and system model

%Seb: I suggest that we give a name to the protocol to be able to refer to it more adequately
\emph{Contributions} We propose a scheme that provides a way for protests to be securely verified.
Additionally, this verification system does not incur any additional risk to 
protesters' privacy than participating in the physical protest itself.

In contrast to the traditional assumption of honest verifiers in
distance-bounding algorithms, we propose a way to turn the Schnorr
protocol into a distance-bounding protocol that allows for a malicious
verifier. In addition, this allows us to form distance-bounding
anonymous credentials.

\subsection{Limitations and Assumptions}

We can achieve privacy, but not receipt freeness.
This means that there is a way for Eve to efficiently verify that Alice has 
participated.
However, this requires that Eve gets a copy of Alice's secret key so that she 
can simply re-do the (deterministic) computations on the same inputs --- the 
probability of collisions is negligible.

%\dots

Some of our assumptions (see Section \ref{assumptions} for more
detailed descriptions) are not yet
realized. Not all (or even many) protesters, especially in countries
with oppressive regimes, currently possess smartphones. Digital
certificates signed by a central authority are not yet widely
available and if we rely on government-issued credentials, we cannot prevent the government 
from performing Sybil attacks --- since it can issue arbitrarily many 
\emph{valid} credentials. In this case we cannot verify any pro-government protests where Eve's authoritarian regime wants to organize a pro-regime protest to 
demonstrate its \emph{wide 
  support}~\cite[e.g.][]{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
Distance bounding on phones is currently not feasible within a
meaningful range of distance for our scenario.

The assumptions might
become sufficiently realistic in the near future, though, with
smartphone penetration on the rise, increased digitalization and government-issued credentials
available in some countries already now (e.g., Estonia, Germany), and
distance-bounding chips~\footnote{ https://www.3db-access.com } currently available with a range of 200 m that
might not unrealistically be integrated in phones or smartcards in the
future.

\emph{Outline.} The paper is organized as follows. 
First, we define the system model for verifiable privacy-preserving crowd counting.  We then
present the desired security properties for such a system and subsequently discuss related
work in terms of these properties. We give the relevant background on
the building blocks of our solution and then describe our proposal for
distance-bounding anonymous credentials that copes with a malicious
(impersonating) verifier. We then present the protocol constructed
from the building blocks, its security and privacy analysis, and
finally our conclusions.

%Seb: I suggest that we move this part to system model
\subsection{Combining properties of electronic voting with location proofs}

In general, protesting is very similar to petitions, which in turn are similar 
to voting: all three are many individuals expressing their opinion.
These opinions can be sensitive, e.g.\ cause for discrimination or persecution, 
hence we desire to have similar properties of verification and privacy for 
verifying a protest as there is for voting.

Voting has (generally) three desirable requirements for 
verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
\begin{description}
  \item[Eligibility] anyone can verify that each vote cast is legitimate.
  \item[Universal verifiability] anyone can verify that the result is according 
    to the cast votes.
  \item[Individual verifiability] every voter can verify that their vote is 
    included in the result.
\end{description}
We translate the votes into \emph{proofs of participation}.
Universal and individual verifiability remain the same: anyone can verify the 
participation count by counting the proofs.
The eligibility requirement is slightly different:
for protests the eligibility requirement must include temporal and spatial 
eligibility, i.e.\ that each proof of participation satisfies some temporal and 
spatial relation to the protest.
In essence, the proof must bind the person to the time and location of the 
protest.
We will define these more formally in \cref{Verifiability}.

There are also three levels of 
privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{itemize}
  \item\label{VotePrivacy} Vote privacy: the voting does not reveal any 
    individual vote.
  \item\label{ReceiptFreeness} Receipt freeness: the voting system does not 
    provide any data that can be used as a proof of how the voter voted.
  \item\label{CoercionResistance} Coercion resistance: a voter cannot cooperate 
    with a coercer to prove the vote was cast in any particular way.
\end{itemize}
We note that we cannot actually improve the privacy of participating protesters during 
the protest: if Alice is caught during a protest or other
crowd-counting mechanisms based on photographic or video evidence are
used to identify Alice, there is nothing we
can do. In our proposed solution, however, we aim at verifiable
participation count that does not add any threats to the participants'
privacy. For instance, if there are counter-protests in the \emph{same location at the same 
  time}, Alice could even blend into another crowd and argue that she participated in 
a different protest than she actually did --- and the counts would still be 
correct afterwards.
However, even if there is only one protest and she is not caught in the act, 
then using our proposed mechanism should not incur any additional risk.
Thus we need at least participation-proof privacy but receipt freeness (see 
\cref{Privacy} for a detailed definition) is desired.
In essence, upon completing the protocol, Eve cannot link Alice to Alice's 
participation proof --- even if she were to compromise Alice's
devices.
%Sonja says: I'm confused: can we or can we not provide this?

>>>>

%Seb: I suggest that we move this part to system model
%\subsection{Combining properties of electronic voting with location proofs}
\emph{Relationship between protesting and electronic voting}. In general, protesting is very similar to petitions, which in turn are similar to voting: all three situations correspond to many individuals expressing their opinion.
These opinions can be sensitive (\emph{e.g.}, be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there is for voting.

Voting has (generally) three desirable requirements for verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
\begin{description}
  \item[Eligibility]: anyone can verify that each vote cast is legitimate.
  \item[Universal verifiability]: anyone can verify that the result is according to the cast votes.
  \item[Individual verifiability]: every voter can verify that their vote is included in the result.
\end{description}
We translate the votes into \emph{proofs of participation}.
Universal and individual verifiability remain the same: anyone can verify the participation count by counting the proofs.
The eligibility requirement is slightly different: for protests the eligibility requirement must include temporal and spatial 
eligibility (\emph{i.e.}, each proof of participation satisfies some temporal and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.
We will define these more formally in \cref{Verifiability}.

There are also three levels of privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{description}
  \item[VotePrivacy]: the voting does not reveal the individual vote.
  \item[ReceiptFreeness]: the voting system does not provide any data that can be used as a proof of how the voter voted.
  \item[CoercionResistance]: a voter cannot cooperate with a coercer to prove the vote was cast in any particular way.
\end{description}
We note that we cannot actually improve the privacy of participating protesters during the protest: if Alice is caught during a protest or other crowd-counting mechanisms based on photographic or video evidence are used to identify Alice, there is nothing we can do. 
%Seb: suggestion maybe we should put the following part in the discussion
However, in \PRIVO, we aim at verifiable participation count that does not add any threats to the participants' privacy. 
For instance, if there are counter-protests in the \emph{same location at the same time}, Alice could even blend into another crowd and argue that she participated in a different protest than she actually did --- and the counts would still be correct afterwards.
However, even if there is only one protest and she is not caught in the act, then using our proposed mechanism should not incur any additional risk.
Thus we need at least participation-proof privacy but receipt freeness (see \cref{Privacy} for a detailed definition) is desired.
In essence, upon completing the protocol, Eve cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device.
%Sonja says: I'm confused: can we or can we not provide this?
%Seb: I agree with Sonja, it is not clear whether we achieve it or not

%Seb: to do complete the contributions
\emph{Contributions.} In this paper, our main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
Additionally, this verification system does not incur any additional risk to protesters' privacy apart from the ones related to participating physically to the protest itself.

In contrast to the traditional assumption of honest verifiers in distance-bounding algorithms, we propose a way to turn the Schnorr protocol into a distance-bounding protocol that allows for a malicious verifier.
%Seb: above, we should put the reference to the Schnorr protocol 
In addition, this allows us to form distance-bounding anonymous credentials.

\emph{Limitations and assumptions.} Some of the assumptions that are required for implementing our proposition are not yet realized (see \cref{assumptions} for more detailed descriptions). 
In particular, not all (or even many) protesters, especially in countries with oppressive regimes, currently possess smartphones.
In addition, digital certificates signed by a central authority are not yet widely available and if we rely on government-issued credentials, we cannot prevent the government from performing Sybil attacks --- since it can issue arbitrarily many \emph{valid} credentials. 
%Seb: maybe to prevent the above issue, we could require the individual to generate his secret key and only use the authority to obtain a certification on his public key (in the spirit of blind signature)
In this case, it does not make sense to verify any pro-government protests in which Eve's authoritarian regime wants to organize a pro-regime protest to demonstrate its wide support~\cite[e.g.][]{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
Finally, achieving distance-bounding protocols on smartphones is currently not feasible within a meaningful range of distance for our scenario.

However, we believe that some assumptions might become sufficiently realistic in the near future, due to the smartphone penetration being on the rise and the increased digitalization and government-issued credentials available in some countries already now (\emph{e.g.}, Estonia and Germany)
In addition, the distance-bounding chips\footnote{\url{https://www.3db-access.com}} currently available can already enable proofs of proximity with a range of 200 meters.
One of the short-term objective is to be able to integrate them in phones or smartcards in the near-future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results~\cite{DBonSmartphones}.

\PRIVO achieve privacy, but not receipt freeness.
This means that there is a way for Eve to efficiently verify that Alice has to the participated.
However, this requires Eve to be able to get a copy of Alice's secret key so that she can simply re-do the (deterministic) computations on the same inputs (the probability of collisions being negligible).

%Seb: to do, update the outline
\emph{Outline.} The paper is organized as follows. 
First, we define and formalize the notion of protest and discuss how is relationship with electronic voting in \cref{SystemModel}.  
We then present the desired security properties for such a system and subsequently discuss related work in terms of these properties. 
We give the relevant background on the building blocks of our solution \PRIVO and then describe our proposal for distance-bounding anonymous credentials that copes with a malicious (impersonating) verifier. 
Finally, we present the protocol constructed from the building blocks, its security and privacy analysis, and finally we conclude by a discussion.
